EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
Removed network section

\begin{lstlisting}[caption=ecs-params.yml , label=code:ecs]
version: 1
task_definition:
  task_execution_role: ecsTaskExecutionRole
  ecs_network_mode: awsvpc
  task_size:
    mem_limit: 8GB
    cpu_limit: 4096
run_params:
  network_configuration:
    awsvpc_configuration:
      subnets:
        - "subnet-0ca2a542bbd74239e"
        - "subnet-0dfd367b5ca531b07"
      security_groups:
        - "sg-0681c18469874b391"
      assign_public_ip: ENABLED
\end{lstlisting}
% Do you need the details about the subnets? As long as they are here, you'll have to explain them. Why two subnets? It's probably better to leave that network configuration out anyway - JJ

% Please clarify that those images are published in Docker hub by yourself - JJ

>>>>

\begin{lstlisting}[caption=ecs-params.yml , label=code:ecs]
version: 1
task_definition:
  task_execution_role: ecsTaskExecutionRole
  ecs_network_mode: awsvpc
  task_size:
    mem_limit: 8GB
    cpu_limit: 4096
\end{lstlisting}
% Do you need the details about the subnets? As long as they are here,
% you'll have to explain them. Why two subnets? It's probably better to
% leave that network configuration out anyway - JJ
% Ok, I removed that section. those parameters are required, but are used 
% internally by the cluster. - M 
% The security group was required to have external access to redis. - M
% Please clarify that those images are published in Docker hub by yourself - JJ
% I have done this a few commits back. (4 paragraphs up) - M
